An Early Eocene temperature gradient modelled with geological and ecological proxies

### 2022-10-14 manuscript/manuscript.Rmd
geochem update

Geochemical climate proxy data were extracted from a latest Paleocene and early Eocene compilation [@hollis2019]. This compilation provides four different geochemical proxies for reconstructing seawater temperature: d180, d47, Mg/Ca and TEX86. For our analyses, this dataset was restricted to the EECO and contains four commonly used geochemical climate proxies: d180, d47, Mg/Ca and TEX_86_ (REFS). For a detailed description of each proxy see [@hollis2019].

@@

>>>>

Geochemical climate proxy data were extracted from a latest Paleocene and early Eocene compilation [@hollis2019]. This compilation provides four different geochemical proxies for reconstructing seawater temperature: $\delta^18^O, \Delta$_47_, Mg/Ca and TEX_86_. For our analyses, this dataset was restricted to the EECO and samples from shallow. We also excluded recrystallised $\delta^18^O samples as secondary diagenetic calcite precipitated after deposition can bias isotope measurements and offset temperature values [@schrag1999].

 For a detailed description of each proxy see [@hollis2019].

@@

To test whether our logistic regression model can adequately describe latitudinal temperature gradients, we applied a simplified version of the model to modern sea surface temperatures from Bio-Oracle [@...]

the climate model is able to estimate latitudinal temperature gradients from limited data, we subsampled modern sea surface temperatures from the Bio-Or
